Approximation as Differentiation

### 2025-03-31 notes/sec/some-categories-with-biproducts.tex
Enough setup to give the CMon-enrichment instance for LatGal.

Define the category $\LatGal$ where:
\begin{itemize}
\item objects $X, Y$ are the bounded lattices;
\item morphisms $f \vdash g: X \to Y$ are meet-semilattice homomorphisms $f: X \to Y$ paired with
join-semilattice homomorphisms $g: Y \to X$ satisfying $y \leq f(x) \iff g(y) \leq x$ for any $x \in X$ and any
$y \in Y$.
\end{itemize}

\noindent $\LatGal$ has finite biproducts.

>>>>

\begin{definition}[Bounded lattice]
A \emph{bounded lattice} $X = (X, \meet, \top, \join, \bot)$ is a partial order $X$ equipped with binary
operations $\meet$ and $\join$ and distinguished elements $\top$ and $\bot$ such that $(X, \meet, \top)$ is a
bounded meet-semilattice and $(X, \join, \bot)$ is a bounded join-semilattice.
\end{definition}

\noindent Since $(X, \meet, \top)$ is a commutative monoid, and thus a $\CMon$-enriched poset category, for
any $X, Y$ there is a zero meet-semilattice homomorphism $0_{X,Y}: X \to \top_Y$ and addition of homomorphisms
$X \to Y$ given by pointwise application of $\meet$. The dual construction applies to $(X, \join, \bot)$. Now
define the category $\LatGal$ where:
\begin{itemize}
\item objects $X, Y$ are the bounded lattices;
\item morphisms $f \vdash g: X \to Y$ are meet-semilattice homomorphisms $f: X \to Y$ paired with
join-semilattice homomorphisms $g: Y \to X$ satisfying $y \leq f(x) \iff g(y) \leq x$ for any $x \in X$ and any
$y \in Y$.
\end{itemize}

\noindent $\LatGal$ is itself $\CMon$-enriched; for any $X, Y$ we have that $\LatGal(X,Y)$ is a commutative
monoid, with:
\begin{itemize}
\item $0_{X,Y}$ is the Galois connection $0_{X,Y} \vdash 0_{Y,X}: X \to Y$
\end{itemize}

\noindent And moreover has finite biproducts:
